---
name: Denise
surname: Piechnik
position: "Data Scientist"
#address: "School of Physics & Chemistry, École Normale Supérieure"
#phone: +1 22 3333 4444
pronouns: she/her
profilepic: mariecurie.jpg
www: mariecurie.com
email: "piechnik.da@gmail.com"
#twitter: mariecurie
github: piechnik-d
linkedin: dapiechnik
date: "`r format(Sys.time(), '%B %Y')`"
aboutme: "I am an experienced project manager with experince in data analytics, database creating and GIS."
output: vitae::twentyseconds
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
```

# Some stuff about me

 * Accomplished ecologist with expertise in research, project management, and data analysis of spatial and tabular data as exemplified by 15 years of experiences in distinguished organizations.
 * Adept at statistics analysis using R programming, Python, Tableau, Arc Geographic Information Systems geospatial tools to analyze stream, forest, biodiversity and land-use data, as described in 11 publications and abstracts.
 * Project manager with demonstrated success leading cross-functional and cross-disciplinary collaborative research, as well as collecting, statistically analyzing, interpreting and reporting results in 2 technical reports and 6 scientific journals. 
# Education
```{r}
library(tibble)
tribble(
  ~ Degree, ~ Year, ~ Institution, ~ Where,
  "Informal studies", "1889-91", "Flying University", "Warsaw, Poland",
  "Master of Physics", "1893", "Sorbonne Université", "Paris, France",
  "Master of Mathematics", "1894", "Sorbonne Université", "Paris, France"
) %>% 
  detailed_entries(Degree, Year, Institution, Where)
```

# Nobel Prizes

```{r}
tribble(
  ~Year, ~Type, ~Desc,
  1903, "Physics", "Awarded for her work on radioactivity with Pierre Curie and Henri Becquerel",
  1911, "Chemistry", "Awarded for the discovery of radium and polonium"
) %>% 
  brief_entries(
    glue::glue("Nobel Prize in {Type}"),
    Year, 
    Desc
  )
```

# Publications

```{r}
library(dplyr)
knitr::write_bib(c("vitae", "tibble"), "packages.bib")

bibliography_entries("packages.bib") %>%
  arrange(desc(author$family), issued)
```

